Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-02 astronum_2019_MAESTROeX/astronum-maestroex.tex
fix spacing

\MarginPar{I feel like someone who knows what they're talking about should write/seriously edit this section}
The latest generation of supercomputers to come online (e.g.~ OLCF Summit, soon NERSC Perlmutter and OLCF Frontier) rely heavily on GPUs in order to achieve high performance while keeping energy consumption to a minimum (GPUs consume considerably less power per flop than CPUs). This trend is set to continue: supercomputers are moving to new architectures in order to increase performance rather than simply adding more and more CPUs. In order for HPC codes to be able to exploit these latest machines, it is therefore becoming increasingly necessary to port codes to run on GPUs.

>>>>

\MarginPar{I feel like someone who knows what they're talking about should write/seriously edit this section}
The latest generation of supercomputers to come online (e.g.\ OLCF Summit, soon NERSC Perlmutter and OLCF Frontier) rely heavily on GPUs in order to achieve high performance while keeping energy consumption to a minimum (GPUs consume considerably less power per flop than CPUs). This trend is set to continue: supercomputers are moving to new architectures in order to increase performance rather than simply adding more and more CPUs. In order for HPC codes to be able to exploit these latest machines, it is therefore becoming increasingly necessary to port codes to run on GPUs.
